% !TEX root = main.tex
\chapter{Introduction}

It's not rocket science.

The following report contains simulations and observations of the hybrid rocket MEOWTH II (\textbf{M}echanical \textbf{E}ngineering \textbf{O}bservational \textbf{W}ingless \textbf{T}utoring \textbf{H}ybrid rocket) created by \emph{Team Rocket} \cite{bulba} at Navitas, Aarhus University. The first rocket was built in 2014 by a previous group of students, but has since been passed along to other students, with the intent of teaching the basics of rocket science.

MEOWTH II was built with the intent of being safer and allow easier data collection. Gorm Bruun Andresen, Alex Nørgaard, a fellow student, and I personally assembled the rocket. The rocket can be seen on the frontpage and on figure \ref{fig:rocketpic}, and each section of the rocket contains at least four possible entrance points for various measurement instruments.

During the previous MEOWTH's tests, a large pressure spike during the startup phase has been observed. This can be seen in the old video here: \url{bit.ly/1SYp1Ug} in the timespan of seconds 5-7. From the video, it appears that just as the rocket exhaust reaches supersonic speeds, \emph{something} explodes, extinguishing the flame. We know it happens before the rocket goes supersonic due to the lack of shock diamonds prior to the event \cite{rockProp}. Tests conducted for this bachelor's thesis can be seen in figure \ref{fig:burnresults}, where all of the four burns start with a large spike in pressure as well.


This bachelor thesis attempts to simulate the rocket's startup condition in order to explain and understand the event. My advisor, Gorm Bruun Andresen, proposed a hypothesis that the pressure spike occurs at the point where mass-flow is choked in the throat. As the flow is sub-sonic, the amount of matter exiting through the nozzle is gradually increasing. When the flow goes sonic or beyond, it is suddenly capped. This abrupt change in physical properties might have been able to explain this event -- that was the hypothesis, but that was quickly rejected after initial simulations. Study revealed that autoignition temperature (the temperature at which materials spontaneously ignite) might be the culprit. The following contains the theories and thoughts that went into simulating the rocket engine's ignition phase, where autoignition temperature is taken into account and attempts to explain the spiking behavior.

The purpose of these simulations are ultimately to improve the rocket and rid it of large pressure variations. To see improvements, it is necessary to measure how the rocket behaves under different conditions. Therefore, setup and calibration of various measurement equipment is essential in order to retrieve excellent data. This is also covered in this report, as the experimental part is of equal importance. The goal is to measure the rocket's inner chamber pressure during firing, and comparing that with simulations. Measuring the rocket chamber's temperature was initially a part of the project as well, but proved to be of great inconvenience. Thermocouples were proposed as a way of doing this, but the very high temperatures are too much for even the strongest of thermocouples \cite{thermocoup}. After studying various methods, a solution using the changing resistivity of glassy-carbon was found, albeit not in time for the launch day. In the final days of the project, a new way of measuring extremely high temperatures was discovered by Gorm, using ultrasonic thermometry \cite{ultrasonic}.
 

All measurements and tests could not have been carried out if not for the test facilities provided by Peter Madsen of Raketmadsen's spacelaboratory. MEOWTH II's tests were carried out on the 3rd to the 4th of May, 2016 in Copenhagen.

The entire project is publicly available on \url{https://github.com/carlegroen/bachelors_degree}, where all work files, data and various notes can be found.


